---
title: "Vid Game Analyses"
output: html_notebook
---

**Import the required libraries.**

```{r}
library(caret)
library(DMwR)
library(ggplot2)
library(reshape2)
library(GGally)
library(dummies)
```

**Read in the data.**

```{r}
vg <- read.csv('vid_games.csv', stringsAsFactors = FALSE)
```

**Reshape the data so I can make histograms with them.**

```{r}
sales <- melt(vg, id = c("Publisher"), measure.vars = c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales"))
names(sales) <- c("Publisher", "Region", "sales")
```

```{r}
global_hist <- ggplot(sales, aes(x = sales))
global_hist + geom_histogram(colour = "blue", fill = "white", binwidth = 0.75, bins = 50) + facet_wrap(~Region)
```

```{r}
global_hist2 <- ggplot(sales, aes(x = log(sales)))
global_hist2 + geom_histogram(colour = "blue", fill = "white", binwidth = 0.75, bins = 50) + facet_wrap(~Region)
```

**Convert some of the variables into factors.**

```{r}
vg$Genre <- as.factor(vg$Genre)
vg$Platform <- as.factor(vg$Platform)
```

**Create some dummy variables for each platform, bind them back into the main data frame.**

```{r}
platform <- dummy(vg$Platform)
vg <- cbind(vg, platform)
```

**Run correlations on a subset of the data.**

```{r}
ggcorr(vg[2:9], low = 'lightcyan', mid = 'cyan1', high = 'darkblue', label = TRUE, label_size = 5, geom = 'tile', layout.exp =0)
```

**Clean up the data a little, remove columns that are inimportant or where I could not feasibly impute missing data.**

```{r}
vg<-vg[-c(660,14247),]
vg[c(1:5, 7)] <- NULL
vg[c(9, 11, 12)] <- NULL
```

**I experimented with a log transform here.**

```{r}
#vg$NA_Sales <- log(vg$NA_Sales)
#vg$EU_Sales <- log(vg$EU_Sales)
#vg$JP_Sales <- log(vg$JP_Sales)
#vg$Other_Sales <-log(vg$Other_Sales)
#vg$Global_Sales <-log(vg$Global_Sales)
```

```{r}
unique(vg$Genre)
```

**Relabeled all the genres.**

```{r}
vg$Genre[vg$Genre == "Sports"] <- 1
vg$Genre[vg$Genre == "Platform"] <- 2
vg$Genre[vg$Genre == "Racing"] <- 3
vg$Genre[vg$Genre == "Role-Playing"] <- 4
vg$Genre[vg$Genre == "Puzzle"] <- 5
vg$Genre[vg$Genre == "Misc"] <- 6
vg$Genre[vg$Genre == "Shooter"] <- 7
vg$Genre[vg$Genre == "Simulation"] <- 8
vg$Genre[vg$Genre == "Action"] <- 9
vg$Genre[vg$Genre == "Fighting"] <- 10
vg$Genre[vg$Genre == "Adventure"] <- 11
vg$Genre[vg$Genre == "Strategy"] <- 12
```

**Create a test train split.**

```{r}

split <- createDataPartition(vg$Genre, p = .8, list = FALSE, times = 1)
vg_train <- vg[split,]
vg_test <- vg[-split,]
```

**Set up parameters for my grid search and cross-validation.**

```{r}
mtry <- sqrt(ncol(vg))
tunegrid <- expand.grid(.mtry = mtry)
metric <- 'Accuracy'
control <- trainControl(method = 'repeatedcv', number = 10, repeats = 2, search = 'random', savePredictions = TRUE)
```

**Training two models, one with 15 trees, another with 500 trees in caret.**
```{r}
model_train1 <- train(Genre ~ ., data = vg_train, method = 'rf', trControl = control, tunegrid = tunegrid, metric = metric, ntree = 15, preProcess = c('BoxCox'))

model_train2 <- train(Genre ~ ., data = vg_train, method = 'rf', trControl = control, tunegrid = tunegrid, metric = metric, ntree = 500, preProcess = c('BoxCox'))
```

**Plotting CV results.**

```{r}
plot(model_train1, ylim=c(.3, .4))

```

```{r}
plot(model_train2, ylim=c(.3, .4))
```

**Generating predicted values.**

```{r}
rf_predict <- predict(model_train1, newdata = vg_test)
rf_predict2<- predict(model_train2, newdata = vg_test)
```

**Generating the plots for my confusion matrices (using ggplot)**

```{r}
cf1<-confusionMatrix(rf_predict, vg_test$Genre)
```

```{r}
cf2<-confusionMatrix(rf_predict2, vg_test$Genre)
```

```{r}

actual = as.data.frame(table(vg_test$Genre))
names(actual) = c("Actual","ActualFreq")
actual$Actual <- as.integer(actual$Actual)


confusion = as.data.frame(table(vg_test$Genre, rf_predict))
names(confusion) = c("Actual","Predicted","Freq")
confusion = merge(confusion, actual)
confusion$Actual <- as.integer(confusion$Actual)
confusion$Predicted <- as.integer(confusion$Predicted)
confusion[order(confusion$Actual, confusion$Predicted),]
confusion$Actual<- as.factor(confusion$Actual)
confusion$Predicted <-as.factor(confusion$Predicted)

confusion$Percent = confusion$Freq/confusion$ActualFreq*100
tile <- ggplot() + geom_tile(aes(x=Actual, y=Predicted,fill=Percent),data=confusion, color="black",size=0.1) + labs(x="Actual",y="Predicted")

tile = tile + 
geom_text(aes(x=Actual,y=Predicted, label=sprintf("%.1f", Percent)),data=confusion, size=3, colour="black") +
scale_fill_gradient(low="lightcyan",high="darkblue")

# lastly we draw diagonal tiles. We use alpha = 0 so as not to hide previous layers but use size=0.3 to highlight border
tile = tile + 
geom_tile(aes(x=Actual,y=Predicted),data=subset(confusion, as.character(Actual)==as.character(Predicted)), color="black",size=0.3, fill="black", alpha=0) 
 
#render
tile

```

